\huge SIMULATION-BASED EVALUATION OF SUSCEPTIBILITY DISTORTION CORRECTION METHODS IN DIFFUSION MRI

### 2014-04-23 Publications/2013-ISBI14/poster/00-main.tex
Fixed typos, title in caps

% @Author: oesteban
% @Date:   2014-04-22 08:55:40
% @Last Modified by:   oesteban
% @Last Modified time: 2014-04-23 16:15:17

@@

\title{\huge Simulation-based evaluation of susceptibility distortion correction methods in dMRI}
\author[Esteban et al.]{O. Esteban$^{1,2}$\and%
A. Daducci$^{2}$\and%
E. Caruyer$^{3}$\and%
K. O'Brien$^{4}$\and%
MJ. Ledesma-Carbayo$^{1}$\and%
M. Bach-Cuadra$^{5,2}$\and%
A. Santos$^{1}$}%}
\institute{
$^{1}$~\includegraphics[height=2cm]{logos/BIT.pdf}~\includegraphics[height=2cm]{logos/UPM.pdf}\hfill%
$^{2}$~\includegraphics[height=2cm]{logos/LTS5.pdf}~\includegraphics[height=2cm]{logos/EPFL.pdf}\hfill%
$^{3}$~\includegraphics[height=2cm]{logos/SBIA.pdf}~\includegraphics[height=2cm]{logos/Penn.pdf}\hfill%
$^{4}$~\includegraphics[height=2cm]{logos/CIBM.pdf}~\includegraphics[height=2cm]{logos/UNIGE.pdf}\hfill%
$^{5}$~\includegraphics[height=2cm]{logos/CHUV.pdf}~\includegraphics[height=2cm]{logos/UNIL.pdf}%
}
\date[May 5th, 2012]{May 5th, 2012}

@@

          The evaluation framework includes the phantom distortion module, the three correction
          methodologies, DTI\&HARDI reconstruction methodologies, tractography,
          and a final module to analyse downstream impact on geometry, tractography and connectivity.
          \end{block}
          }
          % ---------------------------------------------------------%
          % end the column
        \end{minipage}
      \end{beamercolorbox}
    \end{column}
    % ---------------------------------------------------------%
    % end the column
  \end{columns}
  \vfill
  \noindent\makebox[\textwidth][l]{
  \begin{minipage}{0.978\textwidth}
      \begin{beamercolorbox}[]{postercolumn}
            \begin{block}{Visual results}
              \begin{figure}
                 \centering
                 \includegraphics[width=\textwidth]{Fig02-Results}
              \end{figure}
            \end{block}
      \end{beamercolorbox}
  \end{minipage}
  }
  \vfill
  \begin{columns}[T,totalwidth=\textwidth]
    \begin{column}{.34\textwidth}
      \begin{beamercolorbox}[center,wd=\textwidth]{postercolumn}
        \begin{minipage}[T]{\textwidth}  % tweaks the width, makes a new \textwidth
          \noindent\parbox[t]{\textwidth}{ % must be some better way to set the the height, width and textwidth simultaneously
            % Since all columns are the same length, it is all nice and tidy.  You have to get the height empirically
            % ---------------------------------------------------------%
            % fill each column with content
            \vfill            
            \begin{block}{Quantitative results}
            \noindent\makebox[\textwidth][c]{%}
            \begin{minipage}[T][][c]{.75\textwidth} 
            \input{../abstract/041-results-table}
            \input{../abstract/042-results-tractography}
            \end{minipage}
            }
            \end{block}
            \vfill
            \begin{exampleblock}{}
            \begin{figure}
                \centering
                \begin{minipage}{0.45\textwidth}
                \centering
                \includegraphics[height=3.5cm]{logos/qrcode-github}
                \caption{\tiny My GitHub}
                \end{minipage}\hfill
                \begin{minipage}{0.45\textwidth}
                \centering
                \includegraphics[height=3.5cm]{logos/qrcode-paper}
                \caption{\tiny Paper}
                \end{minipage}
                \end{figure}
            \end{exampleblock}
          }
        \end{minipage}
      \end{beamercolorbox}
    \end{column}
    % ---------------------------------------------------------%
    % end the column

    % ---------------------------------------------------------%
    % Set up a column 
    \begin{column}{.64\textwidth}
      \begin{beamercolorbox}[center,wd=\textwidth]{postercolumn}
        \begin{minipage}[T]{.95\textwidth} % tweaks the width, makes a new \textwidth
          \parbox[t]{\textwidth}{ % must be some better way to set the the height, width and textwidth simultaneously
            % Since all columns are the same length, it is all nice and tidy.  You have to get the height empirically
            % ---------------------------------------------------------%
            % fill each column with content
          \begin{block}{Conclusions and references}
            \begin{itemize}
              \item In terms of geometry, REB ranked first.
              \item In terms of tractography, visual assessment and
                    quantitative results suggested that FMB and REB perform better.
              \item Only HARDI yielded useful results. DTI-based tractography erroneously
                    estimated crossing and kissing fibers, therefore it was discarded
                    from evaluation.
              \item Connectivity matrices from HARDI were evaluated. Still, a more appropriate
                    phantom is required, presenting its connecting interface
                    densely covered by the seeding regions.
              \item Connectome analyses demand the standardization of
                    processing techniques and pipelining sofware tools to
                    ensure the reproducibility of experiments and the 
                    reliability of results.
            \end{itemize}

>>>>

% @Author: oesteban
% @Date:   2014-04-22 08:55:40
% @Last Modified by:   oesteban
% @Last Modified time: 2014-04-23 16:31:02

@@

\title{\huge SIMULATION-BASED EVALUATION OF SUSCEPTIBILITY DISTORTION CORRECTION METHODS IN DIFFUSION MRI}
\author[Esteban et al.]{O. Esteban$^{1,2}$\and%
A. Daducci$^{2}$\and%
E. Caruyer$^{3}$\and%
K. O'Brien$^{4}$\and%
MJ. Ledesma-Carbayo$^{1}$\and%
M. Bach-Cuadra$^{5,2}$\and%
A. Santos$^{1}$}%}
\institute{
$^{1}$~\includegraphics[height=2cm]{logos/BIT.pdf}~\includegraphics[height=2cm]{logos/UPM.pdf}\hfill%
$^{2}$~\includegraphics[height=2cm]{logos/LTS5.pdf}~\includegraphics[height=2cm]{logos/EPFL.pdf}\hfill%
$^{3}$~\includegraphics[height=2cm]{logos/SBIA.pdf}~\includegraphics[height=2cm]{logos/Penn.pdf}\hfill%
$^{4}$~\includegraphics[height=2cm]{logos/CIBM.pdf}~\includegraphics[height=2cm]{logos/UNIGE.pdf}\hfill%
$^{5}$~\includegraphics[height=2cm]{logos/CHUV.pdf}~\includegraphics[height=2cm]{logos/UNIL.pdf}%
}
\date[May 5th, 2012]{May 5th, 2012}

@@

          The evaluation framework includes the phantom distortion module, the three correction
          methodologies, DTI\&HARDI reconstruction methodologies, streamline tractography,
          and a final module to analyze downstream impact on geometry, tractography and connectivity.
          \end{block}
          }
          % ---------------------------------------------------------%
          % end the column
        \end{minipage}
      \end{beamercolorbox}
    \end{column}
    % ---------------------------------------------------------%
    % end the column
  \end{columns}
  \vfill
  \noindent\makebox[\textwidth][l]{
  \begin{minipage}{0.978\textwidth}
      \begin{beamercolorbox}[]{postercolumn}
            \begin{block}{Visual results}
              \begin{figure}
                 \centering
                 \includegraphics[width=\textwidth]{Fig02-Results}
              \end{figure}
            \end{block}
      \end{beamercolorbox}
  \end{minipage}
  }
  \vfill
  \begin{columns}[T,totalwidth=\textwidth]
    \begin{column}{.34\textwidth}
      \begin{beamercolorbox}[center,wd=\textwidth]{postercolumn}
        \begin{minipage}[T]{\textwidth}  % tweaks the width, makes a new \textwidth
          \noindent\parbox[t]{\textwidth}{ % must be some better way to set the the height, width and textwidth simultaneously
            % Since all columns are the same length, it is all nice and tidy.  You have to get the height empirically
            % ---------------------------------------------------------%
            % fill each column with content
            \vfill            
            \begin{block}{Quantitative results}
            \noindent\makebox[\textwidth][c]{%}
            \begin{minipage}[T][][c]{.75\textwidth} 
            \input{../abstract/041-results-table}
            \input{../abstract/042-results-tractography}
            \end{minipage}
            }
            \end{block}
            \vfill
            \begin{exampleblock}{}
            \begin{figure}
                \centering
                \begin{minipage}{0.45\textwidth}
                \centering
                \includegraphics[height=3.5cm]{logos/qrcode-github}
                \caption{\tiny My GitHub}
                \end{minipage}\hfill
                \begin{minipage}{0.45\textwidth}
                \centering
                \includegraphics[height=3.5cm]{logos/qrcode-paper}
                \caption{\tiny Paper}
                \end{minipage}
                \end{figure}
            \end{exampleblock}
          }
        \end{minipage}
      \end{beamercolorbox}
    \end{column}
    % ---------------------------------------------------------%
    % end the column

    % ---------------------------------------------------------%
    % Set up a column 
    \begin{column}{.64\textwidth}
      \begin{beamercolorbox}[center,wd=\textwidth]{postercolumn}
        \begin{minipage}[T]{.95\textwidth} % tweaks the width, makes a new \textwidth
          \parbox[t]{\textwidth}{ % must be some better way to set the the height, width and textwidth simultaneously
            % Since all columns are the same length, it is all nice and tidy.  You have to get the height empirically
            % ---------------------------------------------------------%
            % fill each column with content
          \begin{block}{Conclusions and references}
            \begin{itemize}
              \item In terms of geometry, REB ranked first.
              \item In terms of tractography, visual assessment and
                    quantitative results suggested that FMB and REB perform better.
              \item Only HARDI yielded useful results. DTI-based tractography erroneously
                    estimated crossing and kissing fibers, therefore it was discarded
                    from evaluation.
              \item Connectivity matrices from HARDI were evaluated. Still, a more appropriate
                    phantom is required, presenting its connecting interface
                    densely covered by the seeding regions.
              \item Connectome analyses demand the standardization of
                    processing techniques and pipelining software tools to
                    ensure the reproducibility of experiments and the 
                    reliability of results.
            \end{itemize}
